%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://animeshpaul91.github.io/My-Resume/}{\Large ANIMESH PAUL}} & Email:  \href{mailto:ani.nitmz@gmail.com}{ani.nitmz@gmail.com}\\
  \href{https://www.linkedin.com/in/animeshpaul91/}{LinkedIn |} 
  \href{https://github.com/animeshpaul91}{Github}& Mobile:  +1-202-460-7195 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University at Buffalo, The State University of New York}{Buffalo, NY}
      {Master of Science in Computer Science and Engineering;  GPA: 3.5/4.0}{Aug 2018 - Feb 2020}
    \resumeSubheading
      {National Institute of Technology, Mizoram}{Aizawl MZ, India}
      {Bachelor of Technology in Computer Science and Engineering;  GPA: 8.8/10.0}{Jul 2011 - May 2015}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Technical Expertise}
 \resumeSubHeadingListStart
 \resumeSubItem{}{
     \textbf{Programming Languages}{: Java, Python, C, C++, Javascript, Typescript, Shellscript.}
     }
 \resumeSubItem{}{
     \textbf{Databases}{: MySQL, SQL Server, PostgreSQL, MongoDB.}
     }
 \resumeSubItem{}{
     \textbf{Software Frameworks \& Tools}{: Spring Boot, Spring MVC, Maven, Tomcat, Linux, Angular, Node Js.}
    }
 \resumeSubItem{}{
     \textbf{Web Technologies}{: HTML5, CSS3, Bootstrap, REST, JSON, XML.}
    }
 \resumeSubItem{}{
     \textbf{Software Development Methodologies}{: Git, SVN, JIRA, Agile, Scrum, TDD, SDLC.}
    }
 \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Visa Inc.}{Highlands Ranch, CO}
      {Software Engineer}{March 2020 - Present}
      \resumeItemListStart
        \resumeItem{}
          {Built and deployed SSO service for Thousand Eyes, a SaaS network infrastructure monitoring application by leveraging its RESTful services. Automated user management has rendered a 100\% decline in fulfillment requests.}
        \resumeItem{}
        {Piloted a fully automated solution for drift management, standardizing config for 30\% of network infrastructure.}
        \resumeItem{}
        {Collaborated in building a scalable python script which performed security remediation on 150+ network devices.}
        \resumeItem{}
        {Developed a data visualization service that displays outages on third party DNS \& CDN service providers.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Visa Inc.}{Highlands Ranch, CO}
      {Software Engineer Intern}{May 2019 - Aug 2019}
      \resumeItemListStart
        \resumeItem{}
          {Optimized the execution time in the inter-datacenter NAS switchover by 50\% using a REST based automation.}
        \resumeItem{}
        {Developed an event logger in a private cloud Spring Boot application, allowing for the easy retrieval of event logs directly to the UI, thereby eliminating the need for rigorous troubleshooting.}
      \resumeItemListEnd

    \resumeSubheading
      {NSE Infotech Services Limited}{Mumbai, India}
      {Programmer Analyst}{Jul 2015 - Aug 2018}
      \resumeItemListStart
      \resumeItem{}
          {Maintained and enhanced an in-house ERP software. Significantly facilitated its integration with active directory by exposing RESTful web services for user on/off boarding, thereby reducing operational toil by 40\%.}
        \resumeItem{}
          {Implemented real-time monitoring with reporting analytics of key metrics for mission-critical applications across 100+ production servers, while achieving a 35\% reduction in the resolution time of critical incidents \& outages.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  \resumeSubItem{e-Commerce App:}
      {Developed a simple e-Commerce online shopping website as a full-stack web application by exposing inventory data from MySQL DB through REST APIs which gets consumed by the frontend app. Implemented features to display product data, search for products, add to shopping cart, checkout cart and form validation. In addition, security features were built by leveraging Okta with OAuth2.0. \emph{(Java, SpringBoot, Angular, Okta)}}
    \resumeSubItem{Big Data Aggregation \& Visualization:}
      {Performed Map Reduce jobs for determining word count \& co-occurrence metrics on textual data. Ranked the top 10 most frequently occurring words on Tableau. \emph{(Python, Map-Reduce)}}
    \resumeSubItem{Simple Dynamo DB:}
      {Built a simple version of Dynamo DB, a distributed and replicated key-value storage in Android, with consistent hashing, node partitioning, data replication, failure recovery and data synchronization. \emph{(Java, Android)}}
  \resumeSubHeadingListEnd

%-------PUBLICATIONS------------------  
\section{Publications}
 \resumeSubHeadingListStart
  \resumeSubItem{}{Animesh Paul,
  \textbf{Positive and Negative Association Rule Mining using correlation threshold and dual confidence approach}, 2nd International Conference on Computational Intelligence in Data Mining, Dec 2015.}
 \resumeSubHeadingListEnd


%---------Teaching/Leadership Experience-------
\section{Certifications}
 \resumeSubHeadingListStart
 \resumeSubItem{}{Amazon Web Services Certified Cloud Practitioner (AWS, 2021).}
 \resumeSubItem{}{Oracle Cloud Infrastructure Foundations Associate (Oracle University, 2020).}
 \resumeSubItem{}{Deep Learning Specialization (deeplearning.ai, 2019).}
 \resumeSubHeadingListEnd
\end{document}
